Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-03 paper.tex
Abstract points out geometry doesn't need to be regenerated if only camera is moving
Abstract explicitly says frame rates rather than just talking about speed

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes using hardware
acceleration have been developed, but they generally require a large amount of
geometry to be created every frame.  This paper investigates whether using
Boolean operations are faster in the simple case where two axis-aligned volumes
intersect.  Although viable options it is shown that two new methods are no
faster than the traditional slicing method.
\end{abstract}

>>>>

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes using hardware
acceleration have been developed, but they generally require a large amount of
geometry to be created every frame.  In the simple case where two axis-aligned
volumes intersect, it is shown that Boolean operations can be used so that
the camera may move without regenerating any geometry.  However, the two
variations presented herein still achieve similar frame rates to that of the
traditional slicing method.
\end{abstract}
